---
title: "famsa-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{famsa-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### Setup
First, we must load the `famsa` package into our current `R` session:

```{r setup}
library(famsa)
library(Biostrings)
```

## Usage

### The simpliest call to the `famsa` function:
Note that umax is a stringset -- available on start (to be moved to examples...).\
The returned object will be of type `XMultipleAlignment` (eg. `DNA`, `AA` or `RNAMultipleAlignment`).
 
```{r, warning = TRUE, error = TRUE, message = TRUE}
famsa(stringset=umax)
```

### Setting output type to a Distance Matrix
The type of the returned object will be of a simple data.matrix representing a distance matrix.
```{r}
famsa(stringset=umax, distance_matrix = TRUE)
```

## Setting output type to a phylogenetic tree
The type of the returned object will be of a phylogenetic tree in a Newick format.
Here it's plotted for better visualisation
```{r, fig.show='hold'}
plot(famsa(stringset=umax, tree = TRUE))
plot(famsa(stringset=umax, tree = TRUE, advanced_settings="-gt upgma"))
```
